Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance

### 2023-05-07 Manuscript/Manuscript.Rmd
MS: edits to NIT-GC morpholino section

To test the in vivo function of NIT-GC1 and NIT-GC2 in cPRC responses, we returned to calcium imaging. 
To interfere with NIT-GC function, we used morpholino-mediated knockdowns. We used two translation-blocking morpholinos for each *NIT-GC* gene and tested knockdown efficiency by immunostaining injected animals with the NIT-GC1 and NIT-GC2 antibodies **(Figure 4---figure supplement 2E,F)**. For both genes, the morpholinos led to a strong reduction in the respective antibody signal, confirming that the morpholinos efficiently knock down translation and at the same time that the antibodies are specific.

In NIT-GC1 morphant larvae, 405 nm light stimulation caused a decrease in calcium levels in the cPRC, but the increase in calcium levels that occurred after the light stimulation was stopped was strongly suppressed **(Figure 4G)**. This result is similar to the response of NOS mutants in cPRC, suggesting that NIT-GC1 mediates depolarising responses after UV stimulation of cPRC by NO and may be involved in extracellular signalling. Interestingly, in NIT-GC2 morphant larvae, an increase in calcium levels occurred immediately after light stimulation **(Figure 4H)**. The different responses of cPRC upon knockdown of NIT-GC1 and NIT-GC2 suggest that there may be different intracellular signalling mechanisms associated with their respective localisations.

>>>>

To test the in vivo function of NIT-GC1 and NIT-GC2 in cPRC responses, we combined calcium imaging with morpholino-mediated knockdowns. We used two translation-blocking morpholinos for each *NIT-GC* gene and tested knockdown efficiency by immunostaining injected animals with the NIT-GC1 and NIT-GC2 antibodies **(Figure 4---figure supplement 2E,F)**. For both genes, the morpholinos led to a strong reduction in the respective antibody signal, confirming efficient knockdown and antibody specificity.

In NIT-GC1 morphant larvae, the delayed activation of cPRCs following 405 nm stimulation did not occur **(Figure 4G)**. This phenotype is similar to the phenotype of *NOS* mutants suggesting that NIT-GC1 acts as the NO sensor in cPRCs to drive their delayed activation. This could occur via increased cGMP production and the opening of a cyclic-nucleotide-gated (CNG) channel specific to cPRCs. 
NIT-GC2 morphant larvae, in contrast, showed a step-up increase in calcium following light stimulation **(Figure 4H)**. The calcium signal decayed during stimulation and was off after light off. These data support an essential role for ciliary-localised NIT-GC2 in suppressing cPRC calcium following its transient rise at stimulus onset. 
Overall, these knockdown experiments revealed different signalling mechanisms for the two NIT-GCs that may be due to their different subcellular localisations.
